Manuscript

### 2022-09-07 analysis/manuscript.Rmd
update supplemental tables

tar_load(proxyMR_comparison_summary_yiyp_adj_SNPmeta_prune)

data <- proxyMR_comparison_summary_yiyp_adj_SNPmeta_prune
data$rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- data$rho_resid + data$gam_beta

@@

df_list <- list(traits_description, MR_result_table, sex_differences_summary, binned_summary, binned_corr_summary)
final_table <- df_list %>% reduce(full_join, by='exposure_ID') %>%
  dplyr::rename(trait_ID = exposure_ID) %>%
  dplyr::rename(trait_description = description) %>%
  dplyr::select(trait_description, trait_ID, everything())

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", row.names=FALSE)
write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Supp Table 6 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 7 paths_summary", append=TRUE, row.names=FALSE)

>>>>

tar_load(proxyMR_comparison_summary_yiyp_adj_SNPmeta_prune)
tar_load(proxyMR_comparison_summary_yiyp_adj_SNPmeta)

data <- proxyMR_comparison_summary_yiyp_adj_SNPmeta
data$rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- data$rho_resid + data$gam_beta

@@

df_list <- list(traits_description, MR_result_table, sex_differences_summary, binned_summary, binned_corr_summary)
final_table <- df_list %>% reduce(full_join, by='exposure_ID') %>% 
  dplyr::rename(trait_ID = exposure_ID) %>%
  dplyr::rename(trait_description = description) %>%
  dplyr::select(trait_description, trait_ID, variable_type, category, n_pairs, 
                pheno_couple_r2, pheno_couple_r, pheno_couple_r_se, everything())

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Supp Table 6 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 7 paths_summary", append=TRUE, row.names=FALSE)
